Evolving Robot Gaits in Hardware: the HyperNEAT Generative Encoding Vs. Parameter Optimization

### 2011-04-15 paper_ecal/platformDetails.tex
Changed to degrees

Robot gaits are executed via a Python \emph{gait function} that takes time (starting at 0) as a single input and outputs a list of nine commanded positions (one for each servo).  To safeguard against limb collision with the robot body,
the robot control code cropped the commands to a safe range.  This
range was [150,~770] for the inner leg servos, [30,~680] for the outer
leg servos, and [392,~623] for the center hip servo.

>>>>

Robot gaits are defined by a Python \emph{gait function} that takes
time (starting at 0) as a single input and outputs a list of nine
commanded positions (one for each servo).  To safeguard against limb
collision with the robot body, the control code cropped the commands
to a safe range.  This range was [-85$^{\circ}$, +60$^{\circ}$] for
the inner leg servos, [-113$^{\circ}$, +39$^{\circ}$] for the outer
leg servos, and [-28$^{\circ}$, +28$^{\circ}$] for the center hip
servo.

%This range was [150,~770] for the inner leg servos, [30,~680] for the outer
%leg servos, and [392,~623] for the center hip servo.
